---
title: "Social Media Channel Performance"
author: "`r Sys.getenv('USER')`"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    code_fold: hide
    fig_width: 6
    fig_height: 4
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE,
                      fig.height=3.5,
                      fig.width=6)

library(tidyverse)
library(lubridate)
library(here)
library(PerformanceAnalytics)
library(plotly)
library(scales)
library(gridExtra)
library(DT)
library(here)

theme_set(theme_bw())

```

## Intro

Exploration of social media data for a variety of owned social media profiles.

### Data

Data summary:

```{r soc}
data <- read_csv(here('data','soc_media_profiles.csv'))
## remove farthest outliers
data_main <- data %>% filter(interactions<7500000)
```

### Explore

Compare number of posts vs interactions

```{r pressure}
data_main %>% ggplot(aes(x=posts, y=interactions, avg_ipp, color=Channel))+geom_point()

```

A few major outliers in terms of interactions. Try with *log y-axis*:

```{r}
## try with log on y-axis
data_main %>% ggplot(aes(x=posts, y=log(interactions), avg_ipp, color=Channel))+geom_point()
```

Try again with log on both axis and regression line:

```{r}
## log both axis plus lm line
data_main %>% ggplot(aes(x=log(posts), y=log(interactions), avg_ipp))+geom_point()+
  geom_smooth(method='lm')
```

Appears to be some reasonable relationship. Breakout linear regression line by Channel to see if varies.

```{r}
data_main %>% ggplot(aes(x=log(posts), y=log(interactions), avg_ipp, color=Channel))+geom_point()+
  geom_smooth(method='lm')
```

Seems to hold overall, with stronger relationship for IG.

Check correlations:

```{r}
ovc <- cor.test(data_main$interactions, data_main$posts)

data_t <- data_main %>% filter(Channel=='Twitter')
data_f <- data_main %>% filter(Channel=='Facebook')
data_i <- data_main %>% filter(Channel=='Instagram')

tc <- cor.test(data_t$interactions, data_t$posts)
fc <- cor.test(data_f$interactions, data_f$posts)
ic <- cor.test(data_i$interactions, data_i$posts)

print("Overall:")
ovc
print("Twitter")
tc
print("Facebook")
fc
print("Instagram")
ic
```

On closer inspection, only Instagram has statistically significant correlation. 